# Prime Asset Report 

```{r echo=FALSE, message=FALSE, error=FALSE}

library(dplyr)
library(tidyr)
library(ggplot2)
library(grid)


documents_df <- read.csv("../data/asset_list_processed.csv")
date_of_extraction <- read.csv("../data/date_of_extraction.csv")


```


Data as of  **`r as.character(date_of_extraction[1,])`**

## General Information 

The `Prime Asset Report` provides information about released Prime assets from a LabCase point of view. 
We only examine assets which are stored in the [main Prime project](https://labcase.softwareag.com/projects/prime/alfresco/documents) in LabCase in one of the methodology-specific folders. Those assets are available to our user base via the GCS Portal search. 

All information below was gathered by extracting file information using the [LabCase Assets API](https://labcase.softwareag.com/projects/labcase/wiki/LabCase_Asset_API). Currently, the API does not support tags. Therefore, only available file metadata information like `date created`, `date modified`, `folder stored` was processed. In contrast, tag information like, for instance, `asset type` or `scope of usage` could not be taken into account. 



* **Total** number of **assets**: **`r nrow(documents_df)`**

## Creation history

All charts in this section deal with the original date the assets were created and stored in the main Prime project.

```{r echo=FALSE, warning=FALSE, fig.width=12}

assets_created_by_year <- documents_df %>%
  count(year_created) %>%
  replace_na(list(year_created = "Unknown")) %>%
  {max_val <<- max(.$n)
  sum_val <<- sum(.$n)
  . }  %>%
  ggplot(aes(year_created, n)) + 
    geom_bar(stat = "identity", fill = "#0899CC") +
    geom_text(aes(label = n), vjust = -0.2) +
    xlab("Year") +
    ylab("Number of assets") +
    ggtitle(paste0("Assets created by year (", sum_val, " overall)")) +
    ylim(0, max_val * 1.02) +
    theme(plot.title = element_text(size = rel(1.2)),
        axis.title = element_text(size = 12),
        axis.text = element_text(size = 10)) +
    theme_bw()


assets_created_by_method <- documents_df %>%
  count(method_acronym) %>%
  {max_val <<- max(.$n)
  sum_val <<- sum(.$n)
  . } %>%
  ggplot(aes(reorder(method_acronym, n), n)) +
    geom_bar(stat = "identity", fill = "#0899CC") +
    geom_text(aes(label = n), hjust = -0.2) +
    xlab("Methodology") +
    ylab("Number of assets") +
    ggtitle(paste0("Assets created by methodology (", sum_val, " overall)")) +
    ylim(0, max_val * 1.06) +
    coord_flip() +
    theme(plot.title = element_text(size = rel(1.2)),
        axis.title = element_text(size = 12),
        axis.text = element_text(size = 10)) +
    theme_bw()


# Layout plots side-by-side on a 2-row-2-column grid
grid.newpage()
# Push viewport to graphic device
pushViewport(viewport(layout = grid.layout(2, 2)))
print(assets_created_by_year, vp = viewport(layout.pos.row = 1:2, layout.pos.col = 1))
print(assets_created_by_method, vp = viewport(layout.pos.row = 1:2, layout.pos.col = 2))


```


```{r echo=FALSE, warning=FALSE, fig.width=10, fig.height=10}

assets_created_by_year_method <- documents_df %>%
  count(year_created, method_acronym) %>%
  group_by(method_acronym) %>%
  mutate(
    method_plus_numb = paste0(method_acronym, " (", sum(n), " overall)")
  ) %>% 
  replace_na(list(year_created = "Unknown")) %>%
  {max_val <<- max(.$n) 
  .} %>%
  ggplot(aes(year_created, n)) +
    geom_bar(stat = "identity", fill = "#0899CC") +
    geom_text(aes(label = n), vjust = -0.2) +
    xlab("Year") +
    ylab("Number of assets") +
    ggtitle("Assets created by methodology and year") +
    ylim(0, max_val * 1.09) +
    facet_wrap(~ method_plus_numb, ncol = 3) +
    theme_bw() +
    theme(axis.text.x = element_text(angle = 30, hjust = 1, vjust = 1))

assets_created_by_year_method


```

